---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# distreg

The `distreg` package is a collection of functions built for distribution regression.  That is, one can estimate the distribution of $Y$ conditional on $X$ using a model for a binary outcome.  For example,
$$
  F_{Y|X}(y|x) = \Lambda(x'\beta)
$$
where $\Lambda$ is some known link function, such as logit.  

This package was formerly called `TempleMetrics`.  For the time being, we are just hosting the package on Github, but it should work just fine for you.  The main methods are:

* `distreg` -- a function to implement distribution regression as in Foresi and Peracchi (1995) <doi:10.2307/2291056> and Chernozhukov, Fernandez-Val, and Melly (2013) <doi:10.3982/ECTA10582>.

* `lldistreg` -- a function to implement a local linear regression (it's local in just one particular variable -- often a ``treatment'')

In either case, it is often useful to convert these estimates into estimates of conditional distributions themselves. This can be done with the function `Fycondx`.  We give some examples below.

## Installation

You can install `distreg` from github with:

```{r gh-installation}
# install.packages("devtools")
devtools::install_github("bcallaway11/distreg")
```

## Example 1

The first example is how to run distribution regression for a single value of $y$ of $Y$.  This example uses the `igm` dataset which is a collection of 500 parent-child pairs of income along with the parent's education level which comes from the Panel Study of Income Dynamics (PSID).

```{r}
library(distreg)
data(igm)
head(igm)
```

```{r}
y0 <- median(igm$lcfincome)
dreg <- distreg(lcfincome ~ lfincome + HEDUC, igm, y0)
dreg
```

## Example 2
In many cases, of primary interest with distribution regression is obtaining $\hat{F}_{Y|X}(y|x)$ for some particular values of $y$ and $x$.  That's what we do in this example.

```{r}
yvals <- seq(quantile(igm$lcfincome,.05,type=1),
quantile(igm$lcfincome,.95, type=1), length.out=100)
dres <- distreg(lcfincome ~ lfincome + HEDUC, igm, yvals)
xdf <- data.frame(lfincome=10, HEDUC="LessHS")
y0 <- yvals[50]
ecdf(igm$lcfincome)(y0)
Fycondx(dres, y0, xdf)
```
This example says that: (1) the fraction of "children" in the dataset with income below `r format(exp(y0),digits=4)` is `r round(ecdf(igm$lcfincome)(y0),2)`, but (2) we estimate that the fraction of children whose parent's income is `r format(exp(10),digits=4)` and have parent's with less than a HS education with income below `r format(exp(y0),digits=4)` is `r round(Fycondx(dres,y0,xdf)[[1]](y0),2)`.

